Meta-analysis Manuscript Wrangling

### 2021-07-13 shared analysis files /manuscript_datavis_22jun21.Rmd
saving changes and trying to figure out which modle structure to go with

## Acclimation with temperature modifiers
```{r, echo=FALSE}
temp_acclimation_model <- rma.mv(yi, vi, data=dat_acclim_ES, mods=~flux_range * mean_temp_reared,
               random = ~1 | study_id / experiment_id/ response_id,
                 method="REML") 
temp_acclimation_model
```

@@

## Acclimation with all modifiers
```{r, echo=FALSE}
acclimation_model<-rma.mv(yi, vi, data=dat_acclim_ES, 
            mods = ~flux_range * mean_temp_reared + exp_age + size + org_level + exposure_temp, 
               random = ~1 |  study_id/ experiment_id/ response_id,
                 method="REML") 
acclimation_model
```

@@

## Non-linear averaging model with all modifiers
```{r, echo = FALSE}
full_var_model <-rma.mv(yi, vi, data=dat_full_var_ES, 
                        mods = ~flux_range * mean_temp_constant + exp_age + size + org_level, 
               random = ~1 |  study_id/ experiment_id/ response_id,
                 method="REML") 
full_var_model
```

@@

```{r, echo=FALSE}
normalized_acclim <- dat_acclim_ES %>% filter(between(yi, -5, 5))
normalized_var <- dat_full_var_ES  %>% filter(between(yi, -5, 5))

dummy_acclim <- rma.mv(yi, vi, data=normalized_acclim, 
               random = ~1 |  study_id/ experiment_id/ response_id,
                 method="REML")
dummy_var <- rma.mv(yi, vi, data=normalized_var, 
               random = ~1 |  study_id/ experiment_id/ response_id,
                 method="REML")

I2_acclim <- i2_ml(dummy_var)
I2_var <-i2_ml(dummy_acclim)

p1 <- orchard_plot(dummy_acclim, mod = "Int", xlab = "Standardised mean difference", transfm = "none", )+
  annotate(geom = "text", x = 0, y = 1.5, label = "Acclimation")+
  annotate(geom = "text", x = -4.7, y = 1.5, label = paste0("italic(I)^{2} == ",
round(I2_acclim[1] * 100, 2)), color = "black", parse = TRUE, size = 5) + annotate(geom = "text",
x = -3.7, y = 1.49, label = "%", color = "black", parse = FALSE, size = 5)

@@

>>>>

## Acclimation with temperature modifiers
```{r, echo=FALSE}
temp_acclimation_model <- rma.mv(yi, vi, data=dat_acclim_ES, mods=~flux_range * mean_temp_reared,
               random = ~1 | study_id / experiment_id/ response_id,
                 method="REML") 
summary(temp_acclimation_model)
```

@@

## Acclimation with all modifiers
```{r, echo=FALSE}
acclimation_model<-rma.mv(yi, vi, data=dat_acclim_ES, 
            mods = ~flux_range * mean_temp_reared + exp_age + size + org_level + exposure_temp +environment, 
               random = ~1 |  study_id/ response_id,
                 method="REML") 
acclimation_model
```

@@

## Non-linear averaging model with all modifiers
```{r, echo = FALSE}

full_var_model <-rma.mv(yi, vi, data=dat_full_var_ES, 
                        mods = ~flux_range * mean_temp_constant + exp_age + size + org_level +environment, 
               random = list(~1 | study_id/ response_id),
                 method="REML") 
full_var_model

pacman::p_load(esc, dmetar)
summary(full_var_model)
convert_z2r(1.3702) #r=0.8787378

summary(acclimation_model)
convert_z2r(6.0093) #r=0.9999879

acclimation_model

##I-SQUARED CALCS FROM ASSINK + WIBBELINK 2016 (doi:10.20982/tqmp.12.3.p154)
n <- length(dat_acclim_ES$vi)
list.inverse.variances <- 1 / (dat_acclim_ES$vi)
sum.inverse.variances <- sum(list.inverse.variances)
squared.sum.inverse.variances <- (sum.inverse.variances) ^ 2
list.inverse.variances.square <- 1 / (dat_acclim_ES$vi^2)
sum.inverse.variances.square <-
sum(list.inverse.variances.square)
numerator <- (n - 1) * sum.inverse.variances
denominator <- squared.sum.inverse.variances -
sum.inverse.variances.square
estimated.sampling.variance <- numerator / denominator
I2_1 <- (estimated.sampling.variance) / (acclimation_model$sigma2[1]
+ acclimation_model$sigma2[2] + estimated.sampling.variance)
I2_2 <- (acclimation_model$sigma2[1]) / (acclimation_model$sigma2[1]
+ acclimation_model$sigma2[2] + estimated.sampling.variance)
I2_3 <- (acclimation_model$sigma2[2]) / (acclimation_model$sigma2[1]
+ acclimation_model$sigma2[2] + estimated.sampling.variance)

amountvariancelevel1 <- I2_1 * 100
amountvariancelevel2 <- I2_2 * 100
amountvariancelevel3 <- I2_3 * 100
amountvariancelevel1 ##16.20628
amountvariancelevel2 ##1.966446e-06
amountvariancelevel3 ##83.79732

n_f <- length(dat_full_var_ES$vi)
list.inverse.variances_f <- 1 / (dat_full_var_ES$vi)
sum.inverse.variances_f <- sum(list.inverse.variances_f)
squared.sum.inverse.variances_f <- (sum.inverse.variances_f) ^ 2
list.inverse.variances.square_f <- 1 / (dat_full_var_ES$vi^2)
sum.inverse.variances.square_f <-
sum(list.inverse.variances.square_f)
numerator_f <- (n_f - 1) * sum.inverse.variances_f
denominator_f <- squared.sum.inverse.variances_f -
sum.inverse.variances.square_f
estimated.sampling.variance_f <- numerator_f / denominator_f
I2_1f <- (estimated.sampling.variance_f) / (full_var_model$sigma2[1]
+ full_var_model$sigma2[2] + estimated.sampling.variance_f)
I2_2f <- (full_var_model$sigma2[1]) / (full_var_model$sigma2[1]
+ full_var_model$sigma2[2] + estimated.sampling.variance_f)
I2_3f <- (full_var_model$sigma2[2]) / (full_var_model$sigma2[1]
+ full_var_model$sigma2[2] + estimated.sampling.variance_f)

amountvariancelevel1f <- I2_1f * 100
amountvariancelevel2f <- I2_2f * 100
amountvariancelevel3f <- I2_3f * 100
amountvariancelevel1f #7.629274
amountvariancelevel2f #15.61584
amountvariancelevel3f #76.75488

count(dat_acclim_ES, resp_units)
count(dat_full_var_ES, resp_units)

dat_acclim_ES %>%

```{r}
#looking at the effects sizes for each categorical moderator not related to temperature...
# acclimation analysis

a <- dat_acclim_ES %>%
  group_by(size) %>%
  summarise(mean_yi = mean(yi),
            mean_vi = mean(vi)) %>%
  ggplot(aes(x=as.factor(size), y=mean_yi, fill = mean_yi > 0))+
  geom_errorbar(aes(ymin=mean_yi-mean_vi, ymax=mean_yi+mean_vi), width=.2)+
  geom_point(size = 4, show.legend = FALSE, pch=21,colour="black")+
  scale_fill_viridis(discrete = TRUE)+
  xlab("Body Size")+
  ylim(-1,3.5)+
  ggtitle("ACCLIMATION")+
  coord_flip()

b <- dat_acclim_ES %>%
  group_by(exp_age) %>%
  summarise(mean_yi = mean(yi),
            mean_vi = mean(vi)) %>%
  ggplot(aes(x=as.factor(exp_age), y=mean_yi, fill = mean_yi > 0))+
  geom_errorbar(aes(ymin=mean_yi-mean_vi, ymax=mean_yi+mean_vi), width=.2)+
  geom_point(size = 4, show.legend = FALSE, pch=21,colour="black")+
  scale_fill_viridis(discrete = TRUE)+
  xlab("Age")+
  ylim(-1,0.75)+
  coord_flip()

c <- dat_acclim_ES %>%
  group_by(environment) %>%
  summarise(mean_yi = mean(yi),
            mean_vi = mean(vi)) %>%
  ggplot(aes(x=as.factor(environment), y=mean_yi, fill = mean_yi > 0))+
  geom_errorbar(aes(ymin=mean_yi-mean_vi, ymax=mean_yi+mean_vi), width=.2)+
  geom_point(size = 4, show.legend = FALSE, pch=21,colour="black")+
  scale_fill_viridis(discrete = TRUE)+
  xlab("Environment")+
  ylim(-1,0.5)+
  coord_flip()

# assay analysis
d <- dat_full_var_ES %>%
  group_by(size) %>%
  summarise(mean_yi = mean(yi),
            mean_vi = mean(vi)) %>%
  ggplot(aes(x=as.factor(size), y=mean_yi, fill = mean_yi > 0))+
  geom_errorbar(aes(ymin=mean_yi-mean_vi, ymax=mean_yi+mean_vi), width=.2)+
  geom_point(size = 4, show.legend = FALSE, pch=21,colour="black")+
  scale_fill_viridis(discrete = TRUE)+
  xlab("Body Size")+
  ylim(-1,3.5)+
  ggtitle("ASSAY")+
  coord_flip()

e <- dat_full_var_ES %>%
  group_by(exp_age) %>%
  summarise(mean_yi = mean(yi),
            mean_vi = mean(vi)) %>%
  ggplot(aes(x=as.factor(exp_age), y=mean_yi, fill = mean_yi > 0))+
  geom_errorbar(aes(ymin=mean_yi-mean_vi, ymax=mean_yi+mean_vi), width=.2)+
  geom_point(size = 4, show.legend = FALSE, pch=21,colour="black")+
  scale_fill_viridis(discrete = TRUE)+
  xlab("Age")+
  ylim(-1,0.75)+
  coord_flip()

f <- dat_full_var_ES %>%
  group_by(org_level) %>%
  summarise(mean_yi = mean(yi),
            mean_vi = mean(vi)) %>%
  ggplot(aes(x=as.factor(org_level), y=mean_yi, fill = mean_yi > 0))+
  geom_errorbar(aes(ymin=mean_yi-mean_vi, ymax=mean_yi+mean_vi), width=.2)+
  geom_point(size = 4, show.legend = FALSE, pch=21,colour="black")+
  scale_fill_viridis(discrete = TRUE)+
  xlab("Organization Level")+
  ggtitle("ASSAY")+
  coord_flip()

g <- dat_full_var_ES %>%
  group_by(environment) %>%
  summarise(mean_yi = mean(yi),
            mean_vi = mean(vi)) %>%
  ggplot(aes(x=as.factor(environment), y=mean_yi, fill = mean_yi > 0))+
  geom_errorbar(aes(ymin=mean_yi-mean_vi, ymax=mean_yi+mean_vi), width=.2)+
  geom_point(size = 4, show.legend = FALSE, pch=21,colour="black")+
  scale_fill_viridis(discrete = TRUE)+
  xlab("Environment")+
  ylim(-1,0.5)+
  coord_flip()

acclimation_mods<- a + b + c 
var_mods <- d + e + g

acclimation_mods / var_mods

f

```{r}
full_model_coefficients<- as.data.frame(coef(full_var_model)) %>%
  tibble::rownames_to_column("covariates") %>%
  rename(value = "coef(full_var_model)") %>%
  arrange(desc(value)) %>%
  mutate(coefficients = c("intercept", "experimental age", "fluctuation range:mean temperature",
                          "fluctuation range", "environmentterrestrial", "mean temperature",
                                       "size", "organization level" 
                                      ), 
         lb = c(0.4597, -0.0738, -0.0008, -0.0646, -0.7671, -0.0719, -0.5783, -0.8331), 
         ub= c(2.2806, 0.2150, 0.0031, 0.0227, 0.6876, -0.0214, 0.2861, 0.2738))

label.df_full <- data.frame(coefficients = c("intercept","mean temperature"),
                       value = c(0.35, -0.2))

ggplot(data=full_model_coefficients, aes(x = reorder(coefficients, value),
             y = value,
             fill = value > 0)) +
  geom_errorbar(aes(ymin=lb, ymax=ub), width=.2, size =0.6,
                 position=position_dodge(.95), color = "black")+ 
  geom_point(size = 3, show.legend = FALSE, pch=21,colour="black") +
  labs(x = NULL, y = "Coefficient estimate") +
  scale_fill_viridis(discrete = TRUE)+
  theme_bw()+
  coord_flip()+
  geom_text(data=label.df_full, label = "*", color = "black", size = 6)

acclim_model_coefficients<- as.data.frame(coef(acclimation_model)) %>%
  tibble::rownames_to_column("covariates") %>%
  rename(value = "coef(acclimation_model)") %>%
  arrange(desc(value)) %>%
  mutate(coefficients = c("intercept", "fluctuation range:mean temperature",  "exposure_temp",
                          "experimental age", "mean temperature", 
                          "fluctuation range", "environmentterrestrial","size"), 
         lb = c(3.2855, 0.0140, -0.0030, -0.7078, -0.3457, -0.6700, -2.5526, -1.4671), 
         ub= c(8.6331, 0.0312, 0.0093, 0.5405, -0.1733, -0.2814, 1.0587, 0.1290))

label.df_acclim <- data.frame(coefficients = c("intercept", "fluctuation range:mean temperature", "mean temperature", "fluctuation range"),
                       value = c(3, -0.5, -0.7, -1))

ggplot(data=acclim_model_coefficients, aes(x = reorder(coefficients, value),
             y = value,
             fill = value > 0)) +
  geom_errorbar(aes(ymin=lb, ymax=ub), width=.2, size =0.6,
                 position=position_dodge(.95), color = "black")+ 
  geom_point(size = 3, show.legend = FALSE, pch=21,colour="black") +
  labs(x = NULL, y = "Coefficient estimate") +
  scale_fill_viridis(discrete = TRUE)+
  theme_bw()+
  coord_flip()+
  geom_text(data=label.df_acclim, label = "*", color = "black", size = 6)
```

@@

```{r, echo=FALSE}
#creating orchard plot with trimmed/normalized effect sizes from both datasets
normalized_acclim <- dat_acclim_ES %>% filter(between(yi, -5, 5))
normalized_var <- dat_full_var_ES  %>% filter(between(yi, -5, 5))
#corresponding models
dummy_acclim <- rma.mv(yi, vi, data=normalized_acclim, 
               random = ~1 |  study_id/ response_id,
                 method="REML")
dummy_var <- rma.mv(yi, vi, data=normalized_var, 
               random = ~1 |  study_id/ response_id,
                 method="REML")
#calculating I2 for each of the analyses
I2_acclim <- i2_ml(dummy_var)
I2_var <-i2_ml(dummy_acclim)
#orchard plots 
p1 <- orchard_plot(dummy_acclim, mod = "Int", xlab = "Standardised mean difference", transfm = "none", )+
  annotate(geom = "text", x = 0, y = 1.5, label = "Acclimation")+
  annotate(geom = "text", x = -4.7, y = 1.5, label = paste0("italic(I)^{2} == ",
round(I2_acclim[1] * 100, 2)), color = "black", parse = TRUE, size = 5) + annotate(geom = "text",
x = -3.7, y = 1.49, label = "%", color = "black", parse = FALSE, size = 5)

@@

```{r, echo=FALSE}
#calculating mean effect sizes by mean temperature and flux range for ggplots
mean_temp_acclim <- normalized_acclim %>%
  group_by(mean_temp_reared, flux_range) %>%
  summarise(yi=mean(yi), 
            vi=mean(vi))

mean_var<-normalized_var %>%
  group_by(mean_temp_constant, flux_range) %>%
  summarise(yi=mean(yi), 
            vi=mean(vi))
```

```{r, echo=FALSE}
ggplot(normalized_acclim, aes(y=yi, x=mean_temp_reared, fill=flux_range))+
  geom_line(y=0, linetype = "dashed")+
  geom_jitter(alpha = 0.5, pch=21,size=1, width = 0.7, height = 0.7)+
  geom_errorbar(data=mean_temp_acclim, aes(ymin=yi-vi, ymax=yi+vi), size=.7, width=.4, color = "black")+
  geom_point(data = mean_temp_acclim, size=4, pch=21, colour="black")+
  theme_bw()+
  scale_fill_viridis()+
  ggtitle("Acclimation and fluctuation range")+
  labs(x = "Mean temperature (°C)",
       y ="SMD",
       fill = "Temperature fluctuation range (°C)")+
  theme(legend.position="bottom")

ggplot(normalized_var, aes(y=yi, x=mean_temp_constant, fill=flux_range))+
  geom_jitter(alpha = 0.5, pch=21,size=1, width = 0.3, height = 0.7)+
  geom_line(y=0, linetype = "dashed")+
  geom_errorbar(data=mean_var, aes(ymin=yi-vi, ymax=yi+vi), size=.7, width=.4, color = "black")+
  geom_jitter(data = mean_var, size=4, pch=21, colour="black")+
  theme_bw()+
  scale_fill_viridis()+
  ggtitle("Non-linear averaging + acclimation and fluctuation range")+
  labs(x = "Mean temperature (°C)",
       y ="SMD",
       fill = "Temperature fluctuation range (°C)")+
  theme(legend.position="bottom")

ggplot(normalized_var, aes(y=yi, x=mean_temp_constant, fill=mean_temp_constant))+
  geom_jitter(alpha = 0.5, pch=21,size=1, width = 0.3, height = 0.7)+
  geom_line(y=0, linetype = "dashed")+
  geom_errorbar(data=mean_var, aes(ymin=yi-vi, ymax=yi+vi), size=.7, width=.4, color = "black")+
  geom_jitter(data = mean_var, size=4, pch=21, colour="black")+
  theme_bw()+
  scale_fill_viridis()+
  ggtitle("Non-linear averaging + acclimation and mean temperature")+
  labs(x = "Mean temperature (°C)",
       y ="SMD",
       fill = "Mean temperature (°C)")+
  theme(legend.position="bottom")
```
